NoTitle

### 2017-05-25 SpringerLNCS/sections/Formalization.tex
more proof

\begin{lemma}~\label{lamma0}
$\textit{If } \mtype(m, I, J) = \overline{D} \rightarrow D, \textit{ and } \mbody(m, I, J) = \overline{x}.e, 
 \textit{ then for some } J_0 \textit{ with } I <: J_0, \  \exists C <: D, \textit{ such that }  
 \judgeewf {\overline{x}:\overline{D}, \kwthis:J_0} {e:C} $.
\end{lemma}

\begin{lemma}[Term Substitution Preserves Typing]~\label{lamma1}
$\textit{If } \ \judgeewf {\Gamma, \ \overline{x}:\overline{I_X}} { e : I } \textit{ , and }
\judgeewf {\Gamma} {\overline{y}:\overline{I_Y}} \textit{ where } \overline{I_Y} \subtype \overline{I_X}
\textit{, then } \judgeewf {\Gamma} {[\overline{y}/\overline{x}]e : I'} \textit{ for some } I' \subtype I.
$
\end{lemma}

@@

\begin{proof} ~\\
\noindent \textbf{Case Invk.} 
let \[ e = <J>\new I.m(<\overline{I_E}>\overline{e}) \]	
Suppose \[ \mbody(m, I, J) = (\overline{I_X} \; \overline{x}, I_{E_0} \; e_0) \] 
then \[ e' =  [<\overline{I_X}>\overline{e}/\overline{x}, \; <J>\new I/\kwthis ] e_0 \] 
By rules (T-NEW) and (T-INVK), 
  \[ \judgeewf \Gamma {\new I:I} \quad 
	 \mtype(m, I, J) = \overline{I_X} \rightarrow I_{E_0} \quad 
	 \judgeewf \Gamma {\overline{e} : \overline{Y_E}} \quad
	 \overline{Y_E} \subtype \overline{X} \quad
	 \textit{, for some } \; \overline{Y_E}
  \]
By Lemma~\ref{lamma0},
	\[
	\judgeewf {\Gamma, \overline{x}:\overline{I_X}, \kwthis:J_0} {e_0:I_F} \textit{, for some } J \subtype J_0 \textit{ and } I_F \subtype I_{E_0}
	\]
By Lemma~\ref{lamma1},
	\[
	\judgeewf {\Gamma} {[<\overline{I_X}>\overline{e}/\overline{x}, \; <J>\new I/\kwthis ] e_0  :  I_G} \textit{, for some } I_G \subtype I_F 
	\]
So $I_G <: I_{E_0}$, finally just let $I' = I_G$.

\noindent \textbf{Case PathInvk.}
let \[ e = <J>\new I.K::m(<\overline{I_E}>\overline{e}) \]	
Suppose \[ \mbody(m, I, K) = (\overline{I_X} \; \overline{x}, I_{E_0} \; e_0) \] 
then \[ e' =  [<\overline{I_X}>\overline{e}/\overline{x}, \; <K>\new I/\kwthis ] e_0 \] 
By rules (T-NEW) and (T-INVK), 
  \[ \judgeewf \Gamma {\new I:I} \quad 
	 \mtype(m, I, K) = \overline{I_X} \rightarrow I_{E_0} \quad 
	 \judgeewf \Gamma {\overline{e} : \overline{Y_E}} \quad
	 \overline{Y_E} \subtype \overline{X} \quad
	 \textit{, for some } \; \overline{Y_E}
  \]
By Lemma~\ref{lamma0},
	\[
	\judgeewf {\Gamma, \overline{x}:\overline{I_X}, \kwthis:J_0} {e_0:I_F} \textit{, for some } K \subtype J_0 \textit{ and } I_F \subtype I_{E_0}
	\]
By Lemma~\ref{lamma1},
	\[
	\judgeewf {\Gamma} {[<\overline{I_X}>\overline{e}/\overline{x}, \; <K>\new I/\kwthis ] e_0  :  I_G} \textit{, for some } I_G \subtype I_F 
	\]
So $I_G <: I_{E_0}$, finally just let $I' = I_G$.

\noindent \textbf{Case Super-Invk.}
let \[ e = \kwsuper.K::m(<\overline{I_E}>\overline{e}) \]	
Suppose \[ \mbody(m, K, K) = (\overline{I_X} \; \overline{x}, I_{E_0} \; e_0) \] 
then \[ e' =  [<\overline{I_X}>\overline{e}/\overline{x}] e_0 \] 
By rules (T-NEW) and (T-INVK), 
  \[ 
	 \mtype(m, K, K) = \overline{I_X} \rightarrow I_{E_0} \quad 
	 \judgeewf \Gamma {\overline{e} : \overline{Y_E}} \quad
	 \overline{Y_E} \subtype \overline{X} \quad
	 \textit{, for some } \; \overline{Y_E}
  \]
By Lemma~\ref{lamma0},
	\[
	\judgeewf {\Gamma, \overline{x}:\overline{I_X}, \kwthis:J_0} {e_0:I_F} \textit{, for some } K \subtype J_0 \textit{ and } I_F \subtype I_{E_0}
	\]
By Lemma~\ref{lamma1},
	\[
	\judgeewf {\Gamma} {[<\overline{I_X}>\overline{e}/\overline{x} ] e_0  :  I_G} \textit{, for some } I_G \subtype I_F 
	\]
So $I_G <: I_{E_0}$, finally just let $I' = I_G$.

>>>>

\begin{lemma}~\label{lemma0}
$\textit{If } \mtype(m, I, J) = \overline{D} \rightarrow D, \textit{ and } \mbody(m, I, J) = \overline{x}.e, 
 \textit{ then for some } J_0 \textit{ with } I <: J_0, \  \exists C <: D, \textit{ such that }  
 \judgeewf {\overline{x}:\overline{D}, \kwthis:J_0} {e:C} $.
\end{lemma}

\begin{lemma}[Term Substitution Preserves Typing]~\label{lemma1}
$\textit{If } \ \judgeewf {\Gamma, \ \overline{x}:\overline{I_X}} { e : I } \textit{ , and }
\judgeewf {\Gamma} {\overline{y}:\overline{I_Y}} \textit{ where } \overline{I_Y} \subtype \overline{I_X}
\textit{, then } \judgeewf {\Gamma} {[\overline{y}/\overline{x}]e : I'} \textit{ for some } I' \subtype I.
$
\end{lemma}

\begin{proof}~\\
\noindent \textbf{Case Var.}
$ e = x \quad I = \Gamma(x) $. \\
If $x \notin \overline{x}$, then the conclusion is immediate, since $[\overline{y}/\overline{x}]x = x$.
On the other hand, if $x = x_i$ and $I = {I_X}_i$, then since $[\overline{y}/\overline{x}]x = [\overline{y}/\overline{x}]x_i = y_i$,
letting $I' = {I_Y}_i$ finishes the case.

\noindent \textbf{Case New.}
$e = \new I$ and there are no term for substitution, the conclusion is obvious.

\noindent \textbf{Case Invk.}

\noindent \textbf{Case PathInvk.}

\noindent \textbf{Case SuperInvk.}

@@

\begin{proof} ~\\
\noindent \textbf{Case Invk.} 
let \[ e = <J>\new I.m(<\overline{I_E}>\overline{e}) \]	
Suppose \[ \mbody(m, I, J) = (\overline{I_X} \; \overline{x}, I_{E_0} \; e_0) \] 
then \[ e' =  [<\overline{I_X}>\overline{e}/\overline{x}, \; <J>\new I/\kwthis ] e_0 \] 
By rules (T-NEW) and (T-INVK), 
  \[ \judgeewf \Gamma {\new I:I} \quad 
	 \mtype(m, I, J) = \overline{I_X} \rightarrow I_{E_0} \quad 
	 \judgeewf \Gamma {\overline{e} : \overline{Y_E}} \quad
	 \overline{Y_E} \subtype \overline{X} \quad
	 \textit{, for some } \; \overline{Y_E}
  \]
By Lemma~\ref{lemma0},
	\[
	\judgeewf {\Gamma, \overline{x}:\overline{I_X}, \kwthis:J_0} {e_0:I_F} \textit{, for some } J \subtype J_0 \textit{ and } I_F \subtype I_{E_0}
	\]
By Lemma~\ref{lemma1},
	\[
	\judgeewf {\Gamma} {[<\overline{I_X}>\overline{e}/\overline{x}, \; <J>\new I/\kwthis ] e_0  :  I_G} \textit{, for some } I_G \subtype I_F 
	\]
So $I_G <: I_{E_0}$, finally just let $I' = I_G$.

\noindent \textbf{Case PathInvk.}
let \[ e = <J>\new I.K::m(<\overline{I_E}>\overline{e}) \]	
Suppose \[ \mbody(m, I, K) = (\overline{I_X} \; \overline{x}, I_{E_0} \; e_0) \] 
then \[ e' =  [<\overline{I_X}>\overline{e}/\overline{x}, \; <K>\new I/\kwthis ] e_0 \] 
By rules (T-NEW) and (T-INVK), 
  \[ \judgeewf \Gamma {\new I:I} \quad 
	 \mtype(m, I, K) = \overline{I_X} \rightarrow I_{E_0} \quad 
	 \judgeewf \Gamma {\overline{e} : \overline{Y_E}} \quad
	 \overline{Y_E} \subtype \overline{X} \quad
	 \textit{, for some } \; \overline{Y_E}
  \]
By Lemma~\ref{lemma0},
	\[
	\judgeewf {\Gamma, \overline{x}:\overline{I_X}, \kwthis:J_0} {e_0:I_F} \textit{, for some } K \subtype J_0 \textit{ and } I_F \subtype I_{E_0}
	\]
By Lemma~\ref{lemma1},
	\[
	\judgeewf {\Gamma} {[<\overline{I_X}>\overline{e}/\overline{x}, \; <K>\new I/\kwthis ] e_0  :  I_G} \textit{, for some } I_G \subtype I_F 
	\]
So $I_G <: I_{E_0}$, finally just let $I' = I_G$.

\noindent \textbf{Case Super-Invk.}
let \[ e = \kwsuper.K::m(<\overline{I_E}>\overline{e}) \]	
Suppose \[ \mbody(m, K, K) = (\overline{I_X} \; \overline{x}, I_{E_0} \; e_0) \] 
then \[ e' =  [<\overline{I_X}>\overline{e}/\overline{x}] e_0 \] 
By rules (T-NEW) and (T-INVK), 
  \[ 
	 \mtype(m, K, K) = \overline{I_X} \rightarrow I_{E_0} \quad 
	 \judgeewf \Gamma {\overline{e} : \overline{Y_E}} \quad
	 \overline{Y_E} \subtype \overline{X} \quad
	 \textit{, for some } \; \overline{Y_E}
  \]
By Lemma~\ref{lemma0},
	\[
	\judgeewf {\Gamma, \overline{x}:\overline{I_X}, \kwthis:J_0} {e_0:I_F} \textit{, for some } K \subtype J_0 \textit{ and } I_F \subtype I_{E_0}
	\]
By Lemma~\ref{lemma1},
	\[
	\judgeewf {\Gamma} {[<\overline{I_X}>\overline{e}/\overline{x} ] e_0  :  I_G} \textit{, for some } I_G \subtype I_F 
	\]
So $I_G <: I_{E_0}$, finally just let $I' = I_G$.
